---
title: "Intro to linear regression"
output: html_document
---
We start by installing the required packages - as well as the data set
```{r setup, include=FALSE}
#install.packages("readr", "tidyverse")
library(tidyverse)
library(readr)
ds <- read_csv("subs survey - jess & Mike to use  - Sheet1.csv")
```

In order to use the data we first need to clean it to ensure it can be properly used
Now we take a look at the data 

```{r}
ds
```

There is so much wrong with this data - most of the fields are in the wrong
format, and the names are far too long to be usable

Time to tidy

```{r}
cleands <- ds %>% 
  mutate(date = as.Date(`Recorded Date`, format = "%d/%m/%Y"), #format as date and strip time
         user_guid = `External Data Reference`, #rename to match bq
         cover_more = `Which areas of content would you like to see the FT cover more?`,
         cover_more_topics = `Q7 - Topics`,
         journalism_score = `Overall, how would you rate our journalism?`,
         formats_datavis = .$`How would you rate the FT on the following? - Data / Visual Journalism (e.g. charts & graphs)



1/7`,
        formats_videos = .$`How would you rate the FT on the following? - Videos



2/7`,
        formats_podcasts = .$`How would you rate the FT on the following? - Podcasts



3/7`,
        formats_newsletters = .$`How would you rate the FT on the following? - Newsletters



4/7`,
        formats_liveblogs = .$`How would you rate the FT on the following? - Live Blogs



5/7`,
        formats_longform = .$`How would you rate the FT on the following? - Longform (The Big read)



6/7`,
        formats_liveevents = .$`How would you rate the FT on the following? - Live events, either online or in-person (FT Live)



7/7`) %>% 
  select(date, 
         user_guid,
         cover_more,
         cover_more_topics,
         journalism_score,
         formats_datavis,
         formats_videos,
         formats_podcasts,
         formats_newsletters,
         formats_liveblogs,
         formats_longform,
         formats_liveevents) %>% 
  mutate(across(5:12, ~factor(.x)))
```

We have now given our variables much cleaner names and told R the types of variables
we are using

We're nearly there with tidying this data. What's left to do is to remove all test 
or non unique values. 

As with behavioural data we use the user guids to determine uniqueness and whether 
the respondent was genuine. For surveys we occasionally get spammers, and there
is always a chance test / practice responses will find its way into the dataset

```{r}
cleands <- cleands %>% 
  drop_na(user_guid) %>% #remove all data without user guids
  distinct(user_guid, .keep_all = T) #ensure only 1 response per user is taken
```

