---
title: "Exploration"
output: html_notebook
---
Before starting out on any survey analysis it is always a good idea to explore
what your data shows.

Let's take a look at the journalistic formats results 

Main focus is to work out whether our different journalistic formats impact satisfaction with our journalism 

```{r}
journo_formats <- cleands %>% 
  select(6:12) %>% 
  pivot_longer(everything()) %>% 
  group_by(name, value) %>%
  summarise(n = n())

journo_formats

ggplot(journo_formats, aes(value, n)) +
  geom_col() +
  facet_wrap(~name)
```

We can see that live events has had hardly any responses due to large number of NAs

We also see that live blogs, podcasts, and videos have a high proportions of nas
as well as do not use these. This is good to keep in mind should we wish to do 
a regression analysis because they will count as missing data

Let's explore further by looking into what % of users are aware of the particular format

```{r}
journo_formats %>% 
  drop_na() %>% 
  mutate(does_use = if_else(value == "I haven't encountered / do not use these", F, T)) %>% 
  group_by(name) %>% 
  summarise(prop = n / sum(n),
            does_use = does_use) %>% 
  group_by(does_use, name) %>% 
  summarise(prop = sum(prop)) %>% 
  filter(does_use == T) %>% 
  ggplot(aes(reorder(name, + prop) , prop)) +
  geom_col() +
  coord_flip()
```